Evaluating approaches to deriving photometric redshift posterior probability distribution functions for \textsc{LSST}

### 2019-03-10 paper/tex/methods.tex
editing EAZY

We describe the algorithms and implementations of the model-based and data-driven codes in Sections~\ref{sec:templatecodes} and \ref{sec:trainingcodes} respectively.
For each approach, we note how it accounts for photometric uncertainties, how it interprets negative fluxes, what its native output format of \pzpdf s is, and what, if any, preprocessing, including validation, of the prior information it performs.

@@

We test three publicly available and commonly used template-based codes, \bpz, \eazy, and \lephare, that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a merit function using the observed and model fluxes.
These three also share the $\chi^{2}$ merit function
\begin{equation}
	\label{eq_temp_chi}
	\chi^{2}(z, T, A) \equiv \sum_{b}^{N_{\rm{filt}}} \left(\frac{F^{\rm{obs}}_{b} - A F^{\rm{mod}}_{b}(T, z)}{\sigma^{\rm{obs}}_{b}}\right)^{2},
\end{equation}
of normalization factor $A$, template $T$, and redshift $z$, which is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which in our case is the \lsst\ $ugrizy$ filters.

@@

\textsc{EAZY}\footnote{\url{https://github.com/gbrammer/eazy-photoz}} \citep[Easy and Accurate Photometric Redshifts from Yale,][]{Brammer:08} is a template-based photo-$z$ code that includes several features that extend the basic $\chi^2$ fit used in many template codes.
The code can fit the observed photometry with SEDs created from a linear combination of a set of templates at each redshift, and the best-fit SED is found by simultaneously fitting one, two or all of the templates by minimizing $\chi^2$.
The minimized $\chi^2(z)$ is then combined with an apparent magnitude prior to obtain the posterior redshift probability distribution.
On examination of the source code for EAZY, it appears that rather than marginalizing across all templates in the $\chi^2$ calculation, \textsc{EAZY} takes only the minimum value of $\chi^2$ at each redshift.
This improper marginalization does not lead to the correct posterior distribution, an implementation issue that will need to be addressed in the future.
%, although some argue that this is not the mathematically correct way of calculating the posteriors.
\textsc{EAZY} can also account for the uncertainties in the templates by adding an empirically derived template error in quadrature as a function of redshift to the flux errors.

In this paper we use the all-templates mode, which fits the photometric data with a linear combination of the five basis templates.
The EAZY architecture cannot accept a template set other than the same five basis templates employed by \texttt{k-correct} when constructing our mock galaxies.
EAZY was thus run using linear combinations of these five templates rather than using the 100 discrete templates shared by the other template-fitting codes.
We employed the $5$ basis templates described in Section~\ref{sec:buzzard}, and set the template error to zero since these same templates were used to produce the simulated catalog photometry. %\red{The quality parameter \texttt{Qz} is...}
The ability to fit for linear combinations of templates highlights an important implementation difference between similar photo-z codes.
The likelihoods include the application of a type-independent apparent magnitude prior estimated from the training data.

\subsubsection{LePhare}\label{sec:lephare}
%(C\'ecile Roucelle, Eric Nuss, Johann Cohen-Tanugi)

>>>>

We describe the algorithms and implementations of the model-based and data-driven codes in Sections~\ref{sec:templatecodes} and \ref{sec:trainingcodes} respectively.
% For each approach, we note how it accounts for photometric uncertainties, how it interprets negative fluxes, what its native output format of \pzpdf s is, and what, if any, preprocessing, including validation, of the prior information it performs.

@@

We test three publicly available and commonly used template-based codes, \bpz, \eazy, and \lephare, that share the standard physically motivated approach of calculating model fluxes for a set of template SEDs on a grid of redshift values and evaluating a merit function using the observed and model fluxes.
These three also share the \chisq\ merit function
\begin{equation}
	\label{eq_temp_chi}
	\chi^{2}(z, T, A) \equiv \sum_{b}^{N_{\rm{filt}}} \left(\frac{F^{\rm{obs}}_{b} - A F^{\rm{mod}}_{b}(T, z)}{\sigma^{\rm{obs}}_{b}}\right)^{2},
\end{equation}
of normalization factor $A$, template $T$, and redshift $z$, which is a sum of observed flux error $\sigma_{b}^{\rm{obs}}$-weighted squared differences between the observed flux $F^{\rm{obs}}_{b}$ and the normalized predicted flux $F^{\rm{mod}}_{b}(T, z)$ in $N_{\rm{filt}}$ photometric filters $b$, which in our case is the \lsst\ $ugrizy$ filters.

@@

\eazy\footnote{\url{https://github.com/gbrammer/eazy-photoz}} \citep[Easy and Accurate Photometric Redshifts from Yale,][]{Brammer:08} extends the basic \chisq\ fit procedure that defines template-fitting approaches.
The algorithm models the observed photometry with a linear combination of template SEDs at each redshift.
The best-fit SED is found by simultaneously fitting one, two, or all of the templates via \chisq\ minimization, which is distinct from marginalizing across all templates.
The minimized \chisq\ likelihood at each redshift is then combined with an apparent magnitude prior to obtain the redshift posterior PDF.
We note that the utilization of the best-fit SED rather than a proper marginalization does not lead to the correct posterior distribution, an implementation issue that has now been identified and will be addressed by the developers in the future.
\eazy\ can account for uncertainty in the template set by adding in quadrature to the flux errors an empirically derived template error as a function of redshift.

The SED-independent apparent magnitude prior was derived empirically from the DC1 training set.
The \eazy\ architecture cannot accept a template set other than the same five basis templates employed by \texttt{k-correct} when constructing the DC1 catalogue.
However, \eazy\ does feature a flexible \texttt{all-templates} mode, which fits the photometric data with a linear combination of the five basis templates.
We set the template error to zero since the same templates were in fact used to produce the DC1 photometry.

\subsubsection{LePhare}
\label{sec:lephare}
%(C\'ecile Roucelle, Eric Nuss, Johann Cohen-Tanugi)
